Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-10-31 1.Paper/Paper.Rmd

Overall, both Heckman-based imputation (1l. and 2l.) models provide less biased estimates of the coefficient parameters in MNAR scenarios, but the random effects estimates on the 1l.heckman are far away from the true values as no cluster information was considered at all.

 Regarding the coverage, the 2l.Heckman imputation method provides the best coverage values across all the $\rho$ scenarios with a coverage level close to the nominal 95\% interval. Even 2l.Heckman is not properly a randomization-valid [@buuren18c] method across all the $\rho$ values it leads to better results in terms of bias and coverage compared to the evalueated methods.

The 2l.Heckman method, by incorporating individual and marginal level information, allows a bias-variance trade off, thus, as it was observed the Heckman IPD separated resulted in better estimates in terms of RMSE than the other methods evaluated.
In particular, the method provides an advantage over the 1l.Heckman method in systematic missingness scenarios, since the latter does not allow to specify any cluster information implicitly, i.e. by adding a group variable in the imputation model. This can be seen in the estimates of the random effects parameters of the 1l.Heckman method, which are more biased than those of the other methods in which cluster information was included.

However, the accuracy (Width) of the 2l.Heckman model is higher than that of the other evaluated methods, which generally increases as $\rho$ moves away from zero. In particular, we noticed in $\beta_2$ that the width was larger in the MAR scenario, when we checked the simulation results, it seems that the high variability came from simulations in which the linear model estimation had singularity problems.

@@

print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment, 
      hline.after = c(-1,0))
```
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed. 
As can be seen in Figure \ref{fig:region} in terms of subregion level prevalence the estimates of the approaches do not differ significantly between methods, however except for the East-Central region, prevalence estimates under the Heckman approach are higher than those estimated using MAR or CC aproaches. 
```{r region,fig.width = 5, fig.asp =.67, fig.pos="!H", fig.cap="\\label{fig:region} Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last"}
plot_dist
```

>>>>

Overall, both Heckman-based imputation (1l. and 2l.) models provide less biased estimates of the coefficient parameters in MNAR scenarios, but the random effects estimates on the 1l.Heckman are far away from the true values as no cluster information was considered at all.
Regarding the coverage, the Heckman-IPD imputation method provides the best coverage values across all the $\rho$ scenarios with a coverage level close to the nominal 95\% interval. Even 2l.Heckman is not properly a randomization-valid (Rubin 1987b) method across all the $\rho$ values it leads to better results in terms of bias and coverage compared to the evaluated methods.

The precision of the Heckman IPD separated seems it is better than the Heckman IPD full version, specially in the MAR scenarios, when we checked simulation results it seems that the high variability on the full version is related to simulations in which singularity fit that it is an indication that the model is over-fitted.

The 2l.Heckman method, by incorporating individual and marginal level information, allows a bias-variance trade off, thus, as it was observed the 2l.Heckman separated resulted in better estimates in terms of RMSE than the other methods evaluated.
In particular, the method provides an advantage over the 1l.Heckman method in systematic missingness scenarios, since the latter does not allow to specify any cluster information implicitly, i.e. by adding a group variable in the imputation model. This can be seen in the estimates of the random effects parameters of the 1l.Heckman method, which are more biased than those of the other methods in which cluster information was included.
However, the accuracy (Width) of the 2l.Heckman model is higher than that of the other evaluated methods, which generally increases as $\rho$ moves away from zero. In particular, we noticed in $\beta_2$ that the width was larger in the MAR scenario, when we checked the simulation results, it seems that the high variability came from simulations in which the linear model estimation had singularity problems.

@@

print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment, 
      hline.after = c(-1,0))
```
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed.

As can be seen in Figure \ref{fig:region} in terms of sub-region level prevalence the estimates of the approaches do not differ significantly between methods, however except for the East-Central region, prevalence estimates under the Heckman approach are higher than those estimated using MAR or CC approaches. 
```{r region,fig.pos="!H",fig.cap="\\label{fig:region} Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last"}
plot_dist
```
